\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome}

%--------------------Section formatting--------------------
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\pagestyle{empty}

\begin{document}

%--------------------Header--------------------
\begin{center}
    {\LARGE Manuel Oelmaier} \\[1mm]
    Eching, Germany \quad
    \faPhone\ +49 1708319223 \quad
    \faEnvelope\ \href{mailto:manuel@oelmaier.eu}{manuel@oelmaier.eu} \\
    \faLinkedin\ \href{https://www.linkedin.com/in/manuel-oelmaier/}{linkedin.com/in/manuel-oelmaier} \quad
    \faGlobe\ \href{https://manueloelmaier.de}{manueloelmaier.de} \quad
    \faGithub\ \href{https://github.com/manuel-Oelmaier}{github.com/manuel-Oelmaier}
\end{center}

%--------------------Profile--------------------
\section*{Profile}
% TODO: Write a brief summary about yourself, your skills, and your career goals.
Computer Science student at the Technical University of Munich specializing in AI. 
Experienced in fine-tuning transformer models, building full-stack applications, and developing practical AI tools. Skilled in Python, Java, and Bash. 
Passionate about responsible AI development, model evaluation, and creating solutions that bridge technical innovation with real-world impact.
%--------------------Education--------------------
\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill 2021 -- 2025 \\
Technical University of Munich, Germany \\ 
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=2em]
    \item Focus: Machine Learning, AI, Software Development
    \item Relevant coursework: Praktikum Next Gen AI, Ethics in Artificial Intelligence, Fundamentals of Programming
\end{itemize}

\vspace{1em}

\noindent \textbf{Abitur} \hfill 2013 -- 2021 \\
Oskar-Maria-Graf Gymnasium, Germany \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=2em]
    \item Focus on mathematics and computer science
    \item \textit{Seminar paper:} Implementation of a KI based on the Minimax algorithm for a self-created game (before AI hype)
\end{itemize}
%--------------------Skills--------------------
\section*{Skills}
\textbf{Technical:} Python, Java, JavaScript/TypeScript, HTML, CSS, C/C++, Bash, SQL \& MongoDB \\
\textbf{Frameworks / Tools:} PyTorch, Git, Linux, Hugging Face \\
\textbf{Areas of Interest:} Artificial Intelligence, Machine Learning, Software Engineering \\
\textbf{Languages:} German, English (B2) \\
\textbf{Soft Skills:} Problem-Solving, Communication, Teamwork

%--------------------Projects--------------------\begin{itemize}[noitemsep, topsep=0pt]

\section*{ latest Projects}

\vspace{1mm} 

\textbf{Praktikum Next Gen AI: Finetuning an AI Model} \hfill 2025
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=2em]
    \item Fine-tuned transformer-based models for generating Python code.
    \item Set up an automated pipeline to evaluate models on multiple test cases.
    \item Improved model performance from 40\% to 75\% on code generation tasks.
    \item Published the model as a Visual Studio Code extension, enabling users to leverage AI capabilities directly within their coding environment.
\end{itemize}

\vspace{1mm} % small space between projects

\noindent \textbf{Learning Website for Theoretical Informatics} \hfill 2025
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=2em]
    \item Collected all multiple-choice questions for the theoretical informatics course at TUM.
    \item Developed a web-based platform for interactive learning and self-assessment.
\end{itemize}

\vspace{1mm}

\noindent \textbf{Chess AI to Mirror My Playing Style} \hfill 2025 -- Ongoing
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=2em]
    \item Collected all personal games from Lichess for training data.
    \item Converted each game into pairs of (board position, next move) and stored in a database.
    \item Currently training a neural network to predict my next move based on the board position.
\end{itemize}

%--------------------Extracurricular--------------------
\section*{Extracurricular Activities}
\begin{itemize}[noitemsep, topsep=0pt]
\item Chess youth trainer at SC Eching: organized engaging sessions for children.
\item Active reader of non-fiction, focusing on philosophy, ethics, and social criticism
\end{itemize}



\end{document}
